Computational tools for representation theory of affine Lie algebras

### 2009-07-22 AffineLieAlgebras/ACMS2009/article.tex
Couple of phrases added into the first setion

Freudenthal formula can be used for affine Lie algebras as well. It was
the main tool for preparation of tables in the book
\cite{kass1990ala}, but the software used by the authors is not
available.

We use new method proposed in the articles
\cite{lyakhovsky1996rra,lyakhovsky2007dub,ilyin812pbc,kulish4sfa}. The
idea is to use recurrent relations for anomalous branching
coefficients based upon summation over special
set of vectors $\Gamma_{\frak{a}\subset \frak{g}} $ called ``fan''.
\begin{equation}
  \label{recurrent-relation}
  k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
    \sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
      \left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
      \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
      +\gamma }^{\left( \mu \right) }\right)   
\end{equation}

>>>>

Freudenthal formula can be used for affine Lie algebras as well. It was
the main tool for preparation of tables in the book
\cite{kass1990ala}, but the software used by the authors is not
available. We introduce our implementation of this algorithm in
section \ref{sec:details-implementation} and compare it
(~\ref{sec:applications}) to the alternative
approach, based on the formula \eqref{eq:2}, which is described below.

We are mostly interested in the use of the new method proposed in the papers
\cite{lyakhovsky1996rra,lyakhovsky2007dub,ilyin812pbc,kulish4sfa}. The
idea is to use recurrent relations for anomalous branching
coefficients based on the summation over the special
set of vectors $\Gamma_{\frak{a}\subset \frak{g}} $ called ``fan''.
\begin{equation}
  \label{recurrent-relation}
  k_{\xi }^{\left( \mu \right) }=-\frac{1}{s\left( \gamma _{0}\right) }\left(
    \sum_{w\in W}\epsilon \left( w\right) \delta _{\xi ,\pi _{\frak{a}}\circ
      \left( w\circ (\mu +\rho )-\rho \right) +\gamma _{0}}+\sum_{\gamma \in
      \Gamma _{\frak{a}\subset \frak{g}}}s\left( \gamma +\gamma _{0}\right) k_{\xi
      +\gamma }^{\left( \mu \right) }\right)   
\end{equation}
